Structure Learning for $\VAR(p)$ Models

### 2019-05-31 paper/paper.tex
Removed todo notes in paper.
Working on simulation methods -- results are terrible.  pw_scg is also not returning strongly causal graphs.

% TODO:
% -- define "DAG"
% -- remove speculative statements
% --

@@

\begin{proof}
  The equivalence $(1) \iff (3)$ is essentially a restatement of the
  definition, but is in line with the seminal work of Geweke
  \cite{geweke1982measurement}, \cite{geweke1984}.

  The equivalence $(3) \iff (5)$ is also immediate from the
  definitions i.e. the projections are equal if and only if the errors
  are equal.

  We have $(4) \iff (5)$ as a result of Lemma
  \ref{lem:conditional_orthogonality_equivalence}, the additional
  equivalence in $(4)$ is apparent since $\H_{t - 1}^i \subseteq \H_{t - 1}^{-j}$.

>>>>

@@

\begin{proof}
  % Geweke uses the log of the ratio of the determinants of the residual variances
  % 
  % The equivalence $(1) \iff (3)$ is essentially a restatement of the
  % definition, but is in line with the seminal work of Geweke
  % \cite{geweke1982measurement}, \cite{geweke1984}.

  $(1) \iff (3)$ is a tautology, and $(3) \iff (5)$ is immediate from the
  definitions i.e. the projections are equal if and only if the errors
  are equal.  We have $(4) \iff (5)$ as a result of Lemma
  \ref{lem:conditional_orthogonality_equivalence}

% , the additional
%   equivalence in $(4)$ is apparent since $\H_{t - 1}^i \subseteq \H_{t - 1}^{-j}$.
